\documentclass[11pt,a4paper]{article}


\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{newpxtext}
\usepackage{newpxmath}
\usepackage{textcomp}
\usepackage{parskip}
\usepackage{a4wide}
\usepackage{float}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{aviatikz}
\usepackage{xfrac}
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{listings}
\usepackage{listingsutf8}
\usepackage{booktabs}
\usepackage{tabularx}

\floatplacement{figure}{htb}
\floatplacement{table}{htb}


\DeclareSIUnit[number-unit-product={}]{\inch}{\text{\textquotedbl}}
%\DeclareSIUnit[number-unit-product={\thinspace}]{\inch}{in}
\DeclareSIUnit{\feet}{ft}
\DeclareSIUnit{\KIAS}{KIAS}

\sisetup{per-mode = symbol}


\lstset{
  language=[LaTeX]{TeX},
  basicstyle=\ttfamily,
  keywordstyle=\fontfamily{lmss}\bfseries,
  tabsize=2,
  inputencoding=utf8/latin1,
  floatplacement=htb}

\lstdefinestyle{block}{
  basicstyle=\ttfamily,
  breaklines,
  breakindent=10pt}

\lstdefinestyle{numberedblock}{
  style=block,
  numbers=left,
  numberstyle=\scriptsize,
  xleftmargin=20pt,
  frame=leftline}


\input{documentation/latex/inst_figure}


\newcommand{\lara}[1]{\textnormal{\textlangle#1\textrangle}}


\title{AviaTi\textit{k}Z}
\author{Mario Haustein}


\begin{document}

\maketitle
\tableofcontents

\section{Introduction}

This package provides a set of commands to draw graphics related for
theoretical flight training courses. It is base in the \texttt{tikz} package.
All drawing commands have to be placed inside a
\texttt{tikzpicture}~environment.

\section{Instruments}
\input{documentation/content/inst_sample}

\clearpage
\subsection{Pitot-Static Instruments}

The pitot-static system consists of two pressure probes. The static port
measures the barometric pressure of the air around the aircraft. The pitot tube
measures the total pressure of the airflow in the direction of flight. The
difference between total and static pressure is called dynamic pressure.

\subsubsection{Altimeter}
\input{documentation/content/inst_altimeter}

\subsubsection{Variometer}
\input{documentation/content/inst_vsi}

\subsubsection{Airspeed Indicator}
\input{documentation/content/inst_asi}

\clearpage
\subsection{Gyroscopic Instruments}

Gyroscopic instruments using spinning masses driven either pneumatically by a
suction pump or electrically. They base on the effect of precession to display
they orientation or turn rate of the aircraft uninfluenced by acceleration
forces.

\subsubsection{Heading Indicator}
\input{documentation/content/inst_hi}

\subsubsection{Turn Coordinator}
\input{documentation/content/inst_tc}

\subsubsection{Attitude Indicator}

\begin{tikzpicture}
\aviainstai[]
\end{tikzpicture}

\clearpage
\subsection{Radio Navigation}

\subsubsection{Automatic Direction Finder}

\begin{tikzpicture}
\aviainstadf[type=rbi,rb=90]
\end{tikzpicture}

\begin{tikzpicture}
\aviainstadf[type=mdi,brng hdg={30}{55}]
\end{tikzpicture}

\begin{tikzpicture}
\aviainstadf[type=mdi,hdg=45,rb=60]
\end{tikzpicture}

\subsubsection{Course Deviation Indicator}

\begin{tikzpicture}
\aviainstcdi[obs=30,ils/dev={0.2}{0.2}]
\end{tikzpicture}

\begin{tikzpicture}
\aviainstcdi[obs=215,vor/radial=30]
\end{tikzpicture}

\begin{tikzpicture}
\aviainstcdi[obs=215,type=vor,vor/radial=200]
\end{tikzpicture}

\subsection{Engine}

\subsubsection{Tachometer}

\subsubsection{Oil Pressure}

\subsubsection{Oil Temperature}

\subsubsection{Cylinder Head Temperature}

\subsubsection{Exhaust Gas Temperature}

\subsubsection{Carburetor Temperature}

\subsubsection{Fuel Quantity}

\subsubsection{Fuel Flow}

\subsubsection{Manifold Pressure}


\end{document}
